% Utshav Paudel — CV (Overleaf-ready, pdfLaTeX)
% Format modeled on the prior CV layout. Single column, A4.
% No em dashes anywhere in body text. En dashes only in date / number ranges.

\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\definecolor{ink}{HTML}{1a1a1a}
\definecolor{accent}{HTML}{1f4ec5}
\definecolor{muted}{HTML}{555555}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\color{ink}

% Section heading: muted, hairline rule across the page just below the text.
\titleformat{\section}
  {\fontsize{13}{15}\selectfont\color{muted}}
  {}{0pt}{}[\vspace{1pt}{\color{muted}\titlerule}\vspace{2pt}]
\titlespacing*{\section}{0pt}{12pt}{1pt}

% Role block. Two lines:
%   bold Company .................... Location
%   italic Role  .................... italic Dates
\newcommand{\role}[4]{%
  \noindent\textbf{#1}\hfill #2\\[1pt]
  \textit{#3}\hfill \textit{#4}\par
  \vspace{2pt}
}

\newenvironment{bullets}{%
  \vspace{-2pt}
  \begin{itemize}[leftmargin=14pt, itemsep=1pt, topsep=2pt, label={\textbullet}]
}{\end{itemize}\vspace{3pt}}

\newcommand{\project}[2]{%
  \noindent\textbf{#1} \textbar{} \textit{#2}\par\vspace{1pt}
}

\begin{document}

% =========================================================
% Header
% =========================================================
\begin{center}
  {\fontsize{22}{26}\selectfont\bfseries Utshav Paudel\par}
  \vspace{3pt}
  {\color{muted}\small AI Engineer specializing in production LLM systems for clinical and healthcare use cases.\par}
  \vspace{4pt}
  Kathmandu, Nepal\par
  \vspace{2pt}
  \href{mailto:utshav.paudel466@gmail.com}{utshav.paudel466@gmail.com} \textbar{}
  \href{https://linkedin.com/in/utshav-paudel}{LinkedIn: utshav-paudel} \textbar{}
  \href{https://github.com/Utshav-paudel}{github.com/Utshav-paudel} \textbar{}
  \href{https://huggingface.co/Utshav}{huggingface.co/Utshav}
\end{center}

% =========================================================
% Education
% =========================================================
\section*{Education}
\role{Madan Bhandari Memorial College}{Kathmandu, Nepal}%
     {Bachelor of Science in Computer Science \& Information Technology}{Apr. 2022 -- Apr. 2026}

% =========================================================
% Experience
% =========================================================
\section*{Experience}

\role{MedForce AI}{London, UK (Remote)}{AI Engineer}{Jun. 2025 -- Present}
\begin{bullets}
  \item AI engineer on a clinical-automation platform deployed in an NHS pilot. Designed the agent architecture and clinical RAG pipeline targeting clinician documentation and decision-support workflows.
  \item Fine-tuned domain-specific LLMs (Mistral 8$\times$22B, Llama~3, Command~R family) on curated hepatology cases for medical reasoning and structured documentation; built clinical evaluation harnesses covering factuality, citation grounding, and hallucination rate.
  \item Cut inference cost and latency for real-time clinical use through various caching techniques (KV cache, prompt caching, semantic response cache), request batching, and quantization; built monitoring for latency, drift, and hallucination signals.
\end{bullets}

\role{Digital-Dandelion}{London, UK (Remote)}{AI Engineer}{Feb. 2024 -- Jun. 2025}
\begin{bullets}
  \item Built a clinical RAG system over EASL liver-disease guidelines using a multi-route retrieval architecture: simple queries served by embedding-based retrieval, complex queries routed to page-indexed advanced RAG. Reached 97\% answer accuracy vs.\ 85\% on a state-of-the-art baseline and cut end-to-end latency by 50\%.
  \item Trained an EfficientNet image-classification system on GCP scoring 30{,}000+ dental websites for modernization; lifted accuracy from 89\% to 95\% via targeted data augmentation and an architecture switch from the prior baseline. Released the dental scraping and extraction datasets on Hugging Face.
  \item Built a multimodal ranking system for JLL evaluating hundreds of commercial real-estate offices via pairwise tournament comparisons across building exterior, interior, workspace, and floor-plan imagery to identify top performers.
  \item Fine-tuned an LLM on hundreds of past winning creative campaigns and creative-director rubrics for Page \& Page (Novo Nordisk account); validated outputs on KPIs spanning relevance, creativity, and brand-fit.
\end{bullets}

\role{Omdena}{New York, USA (Remote)}{Junior Machine Learning Engineer}{Jul. 2023 -- Sep. 2023}
\begin{bullets}
  \item Coordinated a 10--20-person distributed team across multiple timezones building scraping infrastructure that assembled a 46{,}000-article Nepali news corpus, the working dataset for the program's media-representation research.
  \item Built Nepali-language NLP models capturing local idioms to classify how women and marginalized groups are represented in Nepali news media.
  \item Designed a media-diversity scoring model with explicit progress metrics surfaced to research stakeholders.
\end{bullets}

% =========================================================
% Projects
% =========================================================
\section*{Projects}

\project{MeroDaktar (AI-Powered Medical Platform)}{MedGemma 4B, Gemma-3, Voice AI, FastAPI}
\begin{bullets}
  \item Voice-driven patient interviews in Nepali producing preliminary diagnostic reports and appointment booking.
  \item Fine-tuned a custom MedGemma-Nepali multimodal model (4B, Gemma-3 family) for Nepali clinical image-text reasoning; released fp16, 16-bit, and 4-bit variants on Hugging Face.
  \item FastAPI backend handling AI inference and health-record flow with input validation.
\end{bullets}

\project{Llama-3-70B Extractor}{Llama 3 70B, Information Extraction}
\begin{bullets}
  \item Fine-tuned Llama-3-70B-Instruct for structured information extraction from web content; released full-weights, adapter, and 4-bit variants.
  \item Trained alongside two open Hugging Face datasets (Dental\_website\_scraping, Dentalweb\_extraction) used as the source corpus.
\end{bullets}

% =========================================================
% Technical Skills
% =========================================================
\section*{Technical Skills}
\textbf{Languages}: Python, TypeScript, SQL, C++\\
\textbf{AI/ML}: LLMs, RAG, LangChain, NLP, Computer Vision, Fine-tuning\\
\textbf{Cloud \& DevOps}: Google Cloud Platform (GCP), Docker, Git, MLOps\\
\textbf{Frameworks}: PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, FastAPI

% =========================================================
% Open Models & Datasets
% =========================================================
\section*{Open Models \& Datasets}
\textbf{Hugging Face}: \href{https://huggingface.co/Utshav}{huggingface.co/Utshav}. Released models include the \textbf{MedGemma-Nepali} series (medical multimodal, low-resource clinical language) and the \textbf{Llama-3-70B Extractor} (structured information extraction). Open datasets: \textbf{Dental\_website\_scraping} and \textbf{Dentalweb\_extraction} from the Digital-Dandelion work.

% =========================================================
% Selected Writing
% =========================================================
\section*{Selected Writing}
\href{https://utshavpaudel.com.np/blog/your-rag-is-probably-worse-than-you-think-three-ways-to-find-out/}{Your RAG is Probably Worse Than You Think: Three Ways to Find Out} \textbar{} \textit{utshavpaudel.com.np/blog}

\end{document}
